%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters Degree Thesis 
% Use pdflatex to compile  
% Note:
% All document variables are stored in the Thesis.cls file
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, oneside]{Thesis} % The default font size and one-sided printing

\graphicspath{{Pictures/}} % The directory where pictures are stored
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage[square, numbers, url, comma, sort&compress, cite]{natbib}
\hypersetup{urlcolor=black, colorlinks=true} % Colors hyperlinks in black
\title{\ttitle} % Defines the thesis title

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------
\frontmatter % Use Roman page numbering style (i, ii, iii, iv...) for pre-content pages

\begin{titlepage}
\begin{center}

\textsc{\Huge \univname}\\[25pt]\\[2.13cm] 
\textsc{\LARGE \facname}\\[20pt]\\[2.13cm] 
\textsc{\Large \deptname}\\[2.0cm]

\HRule  \\[0.5cm]
{\huge \bfseries \textit{\ttitle}}\\[0.4cm]
\HRule \\[2.0cm] 

\Large \textit{A thesis submitted to the \facname \\ in partial fulfilment of the requirements for the degree of \\ \degreename \\}\\[1.0cm]
\Large \textit{\textbf{ By \\}}\\[0.5cm]
\Large \authornames \\ \textsc{\textit{( SC09B676 )}} }
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------
\Declaration{

\addtocontents{toc}% Add a gap in the Contents

I, \textsc{\authornames}, Matriculation Number (SC09B676) declare that this thesis titled, \textit{\ttitle} and the work presented in it are my own. I confirm that this work was done wholly while in candidature for a \degreename\hspace{2}at the \univname. Where I consulted the published work of others, this has been clearly acknowledged. This work has not been previously submitted for a degree or any other qualification at this University or any other institution.\\[6.0cm]
 
% Allowances for my signature and Date
\begin{minipage}{0.5\textwidth}
\begin{flushleft} 
Signed:\\
\Large
\rule[1em]{10em}{2.0pt} % This prints a line for my signature
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushleft} \Large
\hspace{20} Date:\\
\hspace{20} \rule[1em]{10em}{2.0pt} % This prints a line for the date 
\end{flushleft}
\end{minipage}

% My name and University matriculation number
\begin{flushleft}
\large \textsc{\authornames} \\ \hspace{35}(SC09B676)
\end{flushleft}
}

\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	DEDICATION PAGE
%----------------------------------------------------------------------------------------
\Dedication{
\pagestyle{empty} % No headers or footers for the following pages

\null\vfill % Add some space to move the quote down the page a bit
\begin{center}
\Huge \textit{\textbf{ To My Family }}
\end{center}

\vfill\vfill\vfill\vfill\vfill\vfill\null % Add some space at the bottom to position the quote just right
}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	CERTIFICATION PAGE
%----------------------------------------------------------------------------------------

\Certification{

\addtocontents{toc}

This is to certify that this research project titled \textit{\ttitle} is the original work of \textsc{\authornames}, Matriculation Number (SC09B676), a \degreename\hspace{2} student of the \deptname\hspace{2} in the \facname\hspace{2} at the \univname\hspace{1}.\\[2.5cm]
 
\begin{minipage}{0.5\textwidth}
\begin{flushleft} 
Supervisor:\\
\Large \rule[1em]{10em}{2.0pt} % This prints a line for the signature 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushleft} \Large
\hspace{30} Date:\\
\hspace{30} \rule[1em]{10em}{2.0pt} % This prints a line for the signature
\end{flushleft}
\end{minipage}
\large \textsc{\supname}\\[0.5cm] % Prints my Supervisor's name


\begin{minipage}{0.5\textwidth}
\begin{flushleft} 
HOD/CSC:\\
\Large \rule[1em]{10em}{2.0pt} % This prints a line for the signature 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushleft} \Large
\hspace{30} Date:\\
\hspace{30} \rule[1em]{10em}{2.0pt} % This prints a line for the signature 
\end{flushleft}
\end{minipage}
\large \textsc{Dr Denis Nkweteyim}\\[0.5cm]

\begin{minipage}{0.5\textwidth}
\begin{flushleft} 
Dean/FS:\\
\Large \rule[1em]{10em}{2.0pt} % This prints a line for the signature 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushleft} \Large
\hspace{30} Date:\\
\hspace{30} \rule[1em]{10em}{2.0pt} % This prints a line for the signature
\end{flushleft}
\end{minipage}
\large \textsc{Prof Ayonghe Samuel}

}

\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENT
%----------------------------------------------------------------------------------------
\Acknowledgement{

\addtocontents{toc}% Add a gap in the Contents,

Firstly, I thank our Lord Jesus Christ for giving me
life and good health during my stay at University Of Buea and for
granting me the patience to go through this program.

I am grateful to the Vice Chancellor of the University Of Buea and her collaborators for 
maintaining an enabling environment where graduate students can  
learn and express their utmost research potential. I am especially indebted  
to Professor Joyce B.M. Endeley, currently the Director of the Higher  
Technical Teachers’ Training College of the University of Buea in Kumba  
and Professor Theresa Nkuo­ Akenji, the Deputy Vice Chancellor for  
Internal Control and Evaluation who authorized the connection of internet  
facilities to the Postgraduate Computer Science Laboratory during the  
implementation of this project.   
I wish to sincerely thank all the staff of the Department of Computer  
Science for their advice and stimulating conversations during the writing   of  
this thesis. Special thanks go to Professor Emmanuel Kamgnia and Dr.  
Denis Nkweteyim for meticulously proofreading through and correcting this  
work while making their wide spectrum of research experience and books  
on graphics available to me.

My appreciation goes to the Google Open Source Programs
Office (OSPO) – Mary Radomile, Carols Smith, Cat Allman and
Stephanie Taylor and the United States Army Research Laboratory BRL-CAD team
 for their sponsorship of this project under the auspices
of the 2013 Google Summer Of Code program. Special thanks go
to Mr. Christopher Sean Morrison and Mr. Erik Greenwald for their
valuable advice and mentorship during the implementation of this
project. I am also indebted to \textit{Nominal Animal} and the
mathematician Dr. Titus Piezas for tips on ray-tracing the heart
surface.

Many thanks go to my family for their assistance and
encouragement throughout this program.This thesis is dedicated to them.
I also thank the friends I made during the
course of this program whether from University of Buea or the Developer community,
for bringing all the fun they came along with– I appreciate your
company and I'm happy to know I was not alone.
}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------
\Abstract{

\abstract{\addtocontents{toc}%Add a gap in the Contents

\textit{In this thesis titled \textit{\ttitle}, we aimed at demonstrating the engineering of a primitive within the BRL-CAD package viz the heart-shaped primitive or simply heart-shape.Using a case study approach, we designed the heart-shaped primitive's data structure, wrote necessary callback functions and tested them using BRL-CAD's testing infrastructure. We showed that the Laguerre-based root solver is indeed a sure-fire iterative method for finding roots of polynomials and ascertained it's stability on sextic equations. This work provides a guideline for the development of primitives within Computer Aided Design (CAD) software by highlighting the implementation of geometrically-useful properties for any primitive within BRL-CAD.} \\[0.3cm]
\textbf{Keywords: \textit{\keywordnames}}
}
}

\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\pagestyle{fancy} % Use the "fancy" headers as defined before to bring them back

\lhead{\emph{Contents}}
\tableofcontents % Write out the Table of Contents

\lhead{\emph{List of Figures}}
\listoffigures % Write out the List of Figures

\lhead{\emph{List of Tables}}
\listoftables % Write out the List of Tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------
\Abbreviations{

\addtocontents{toc}%Add a gap in the Contents, for aesthetics

\setstretch{1.5} % Set the line spacing to 1.5, this makes the following tables easier to read
\textbf{CAD} \hspace{25} \textbf{C}omputer \textbf{A}ided \textbf{D}esign \\
\textbf{BRL-CAD} \textbf{B}allistic \textbf{R}esearch \textbf{L}aboratory \textbf{C}omputer \textbf{A}ided \textbf{D}esign \\
\textbf{CSG} \hspace{30} \textbf{C}onstructive \textbf{S}olid \textbf{G}eometry \\
\textbf{NURBS} \hspace{10} \textbf{N}on-\textbf{U}niform \textbf{R}ational \textbf{B}-\textbf{S}plines \\
\textbf{NMG} \hspace{26} \textbf{N}on - \textbf{M}anifold \textbf{G}eometry \\
\textbf{B-REPS} \hspace{10} \textbf{B}oundary \textbf{R}epresentations \\
}
\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

% Include the chapters of the thesis as separate files from the Chapters folder

\input{Chapters/Chapter1}
\input{Chapters/Chapter2} 
\input{Chapters/Chapter3}
\input{Chapters/Chapter4} 
\input{Chapters/Chapter5} 

\clearpage % Start a new page

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY/REFERENCES
%----------------------------------------------------------------------------------------

\label{References}

\lhead{\emph{References}} % Name the Page header "References"

\bibliographystyle{ieeetr} % Use the "ieeetr" BibTeX style for formatting the References

\bibliography{References} % The references information are stored in the file named "References.bib"

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDIX
%----------------------------------------------------------------------------------------

\backmatter
\appendix
\lhead{\emph{Appendix}}

\input{Appendices/Appendix}

\end{document}  
